
\section{Background}
\label{sec:background}
In our research we focused on residents in Mendocino County. Our research is
also
loosely affiliated with Further Reach.

\subsection{Mendocino County}
\label{sec:mendocino-county}

Mendocino is a small county located on the north coast of California. Due to
the remoteness of its location and sparse population, high speed Internet has
not pervasively penetrated this county, much to the frustration of its citizens.
Most people rely on dial-up and satellite connections to access the internet, which proves to be time consuming and unfavorable.


\subsection{Further Reach}
\label{sec:further-reach}

%% The following descriptions are from De Novo Group project description:
%% http://denovogroup.org/main/celerate-project/

The Further Reach/Celerate project is a De Novo Group~\cite{denovo} initiative
to provide affordable broadband Internet access to rural communities around the
world.

Many rural communities remain disconnected or are forced to rely upon slow,
unreliable, or expensive Internet access. While many long-range networks have
been developed in the past to connect such communities, the rollouts of such
networks are fraught with complexities of both deployment and operation, leading
to higher costs and lower reliability for users. Further Reach will leverage work
from the burgeoning area of Software Defined Networking (SDN) to help redefine
how such networks are built and managed.

The initial phase of Internet access rollout will begin with rural communities
in Northern California within 250 miles of the San Francisco Bay Area. This
initial rollout will enable De Novo Group and its affiliated researchers to
provide real Internet access to users while refining new approaches that improve
performance, reliability, and affordability. Beyond this initial series of
deployments, Celerate will expand to communities beyond California, and De Novo
Group will seek to partner with interested technologists around the world.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
